Storm surges in the Strait of Georgia simulated with a regional model

### 2015-05-04 AO_guides/manuscriptAO.tex
formatting data files

\usepackage[natbibapa]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!

@@

\begin{table}[h]
\centering 
\tbl{Evaluation of model performance for all hindcasts presented. Mean absolute error ($\bar{e}$), observed mean (subscript o), modelled mean (subscript m), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and residuals ($\delta$). Statistics are calculated over the time period displayed in each simulation's corresponding figure (three or four days). For the Nov 2006 case, the statistics were calculated over a three day period. The average values were calculated over all of the hindcasts, excluding the Dec 2012 HRDPS simulation. } 
{\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Feb 2006       &                &                      &                      &            &        &                &                        &                        &           &           \\
Point Atkinson & 10.5           & 3.46                 & 3.54                 &   0.012    & 0.996  & 6.2            &  0.273                 & 0.309                  & 0.065     & 0.979     \\
Victoria       &  7.6           & 2.18                 & 2.19                 &   0.032    & 0.992  & 6.1            &  0.235                 & 0.278                  & 0.085     & 0.970     \\
Patricia Bay   &  9.1           & 2.60                 & 2.64                 &   0.024    & 0.992  & 6.8            &  0.223                 & 0.278                  & 0.070     & 0.969     \\
Campbell River & 13.1           & 3.20                 & 3.21                 &   0.041    & 0.990  & 5.8            &  0.303                 & 0.300                  & 0.079     & 0.978     \\
\hline 
Nov 2006       &                &                      &                      &            &        &                &                        &                        &           &           \\
Point Atkinson &  9.8           &  3.42                & 3.43                 &   0.034    & 0.991  &  7.7           &  0.290                 & 0.247                  &  0.128     & 0.950 \\
Victoria       &  9.1           &  2.16                & 2.11                 &   0.070    & 0.978  &  6.2           &  0.222                 & 0.202                  &  0.171     & 0.946 \\
Patricia Bay   & 10.0           &  2.57                & 2.53                 &   0.049    & 0.985  &  6.6           &  0.235                 & 0.203                  &  0.144     & 0.947 \\
Campbell River & 10.7           &  3.20                & 3.26                 &   0.037    & 0.989  &  6.2           &  0.254                 & 0.236                  &  0.140     & 0.952 \\
\hline
Dec 2006       &                &                      &                      &            &        &                &                        &                        &           &           \\
Point Atkinson & 10.5           &  3.45                & 3.47                 &   0.025    & 0.994  & 11.1           &  0.212                 & 0.186                  &  0.275     & 0.891 \\
Victoria       &  9.6           &  2.23                & 2.16                 &   0.042    & 0.984  &  7.9           &  0.190                 & 0.156                  &  0.223     & 0.911 \\
Patricia Bay   &  9.2           &  2.63                & 2.58                 &   0.031    & 0.990  &  9.5           &  0.193                 & 0.149                  &  0.260     & 0.889 \\
Campbell River & 10.6           &  3.23                & 3.28                 &   0.030    & 0.992  &  9.4           &  0.191                 & 0.163                  &  0.247     & 0.905 \\
\hline  
Nov 2009       &                &                      &                      &            &        &                &                        &                        &           &           \\
Point Atkinson & 14.0           &  3.43                & 3.54                 &   0.012    & 0.995  &  5.8           &  0.295                 & 0.316                  &  0.200     & 0.926 \\
Victoria       &  9.9           &  2.25                & 2.23                 &   0.024    & 0.988  &  4.5           &  0.312                 & 0.280                  &  0.211     & 0.911 \\
Patricia Bay   & 10.3           &  2.59                & 2.64                 &   0.019    & 0.997  &  5.6           &  0.265                 & 0.275                  &  0.230     & 0.918 \\
Campbell River & 13.6           &  3.22                & 3.26                 &   0.019    & 0.991  &  4.5           &  0.313                 & 0.297                  &  0.182     & 0.934 \\
\hline 
Dec 2012-CGRF &                &                      &                      &            &        &                &                        &                        &           &           \\ 
Point Atkinson &  9.1           &  3.36                & 3.40                 &   0.006    & 0.998  &  5.0           &  0.300                 & 0.290                  &  0.161     & 0.949 \\
Victoria       & 14.6           &  2.15                & 2.08                 &   0.039    & 0.988  &  4.8           &  0.309                 & 0.274                  &  0.150     & 0.937 \\
Patricia Bay   & 14.2           &  2.55                & 2.51                 &   0.026    & 0.992  &  4.7           &  0.300                 & 0.274                  &  0.140     & 0.945 \\
Campbell River & 11.6           &  3.06                & 3.09                 &   0.013    & 0.996  &  5.7           &  0.241                 & 0.278                  &  0.182     & 0.921 \\
\hline 
Dec 2012-HRDPS &                &                      &                      &            &        &                &                        &                        &           &           \\
Point Atkinson &  8.8           &  3.35                & 3.39                 &   0.006    & 0.998  &  5.4           &  0.300                 & 0.278                  &  0.163     & 0.943 \\
Victoria       & 14.3           &  2.15                & 2.09                 &   0.038    & 0.988  &  4.6           &  0.309                 & 0.277                  &  0.145     & 0.941 \\
Patricia Bay   & 14.0           &  2.55                & 2.52                 &   0.025    & 0.993  &  4.5           &  0.300                 & 0.278                  &  0.130     & 0.953 \\
Campbell River & 11.6           &  3.06                & 3.09                 &   0.014    & 0.993  &  5.6           &  0.241                 & 0.275                  &  0.183     & 0.924 \\
\hline 
\hline
Averages       &                &                      &                      &            &        &                &                        &                        &           &         \\                
Point Atkinson &	10.8	& 3.42	& 3.48	& 0.018	& 0.995	& 7.2	& 0.274	& 0.270	& 0.166	 & 0.939 \\
Victoria       &	10.2	& 2.19	& 2.15	& 0.041	& 0.986	& 5.9	& 0.254	& 0.238	& 0.168	 & 0.935 \\
Patricia Bay   &	10.6	& 2.59	& 2.58	& 0.030	& 0.991	& 6.6	& 0.243	& 0.236	& 0.169	 & 0.934 \\
Campbell River &	11.9	& 3.18	& 3.22	& 0.028	& 0.992	& 6.3	& 0.260	& 0.255	& 0.166  & 0.938 \\
\hline
\end{tabular}}
\label{tab:statistics}
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper production.ipynb and saved in statistics_feb2006.CV 
%I also have standard deviations, correlations, ...

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison of observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson (upper) and Sandheads (lower). Observed winds shown in solid black, low resolution CGRF model in dashed black and high resolution model in grey. Observations are from the Environment Canada Climate Data archives \citep{ECClimateArchive}.}
\label{fig:dec2012_weather}
\end{figure}

>>>>

\usepackage[natbibapa]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!
\usepackage{color}
\usepackage{hyperref}

@@

\begin{table}[h]
\centering 
\tbl{Evaluation of model performance for all hindcasts presented. Mean absolute error ($\bar{e}$), observed mean (subscript o), modelled mean (subscript m), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and residuals ($\delta$). Statistics are calculated over the time period displayed in each simulation's corresponding figure (three or four days). For the Nov 2006 case, the statistics were calculated over a three day period. The average values were calculated over all of the hindcasts, excluding the Dec 2012 HRDPS simulation. } 
{\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Feb 2006& & & & & & & & & &\\ 
Point Atkinson & 11.6& 3.458& 3.558& 0.012& 0.994& 5.5& 0.318& 0.33& 0.058& 0.985\\
Victoria       & 8.2& 2.182& 2.205& 0.035& 0.99& 5.3& 0.276& 0.298& 0.075& 0.979\\
Patricia Bay   & 10.4& 2.601& 2.678& 0.025& 0.99& 5.5& 0.275& 0.298& 0.066& 0.981\\
Campbell River & 12.2& 3.202& 3.235& 0.034& 0.991& 7.0& 0.27& 0.317& 0.066& 0.973\\
\hline
Nov 2006& & & & & & & & & & \\
Point Atkinson & 10.2& 3.422& 3.499& 0.026& 0.99& 6.7& 0.32& 0.305& 0.128& 0.96\\
Victoria       & 7.8& 2.158& 2.182& 0.065& 0.982& 4.7& 0.246& 0.26& 0.134& 0.961\\
Patricia Bay   & 9.4& 2.565& 2.634& 0.043& 0.983& 5.9& 0.258& 0.261& 0.152& 0.953\\
Campbell River & 9.9& 3.201& 3.243& 0.032& 0.991& 6.3& 0.29& 0.293& 0.153& 0.951\\
\hline
Dec 2006& & & & & & & & & & \\
Point Atkinson & 12.9& 3.452& 3.531& 0.028& 0.99& 10.0& 0.336& 0.33& 0.272& 0.895\\
Victoria       & 8.1& 2.229& 2.226& 0.046& 0.988& 7.2& 0.306& 0.3& 0.227& 0.916\\
Patricia Bay   & 10.2& 2.628& 2.674& 0.035& 0.989& 8.8& 0.308& 0.293& 0.255& 0.896\\
Campbell River & 11.3& 3.234& 3.265& 0.034& 0.991& 8.2& 0.311& 0.304& 0.235& 0.912\\
\hline
Nov 2009& & & & & & & & & & \\
Point Atkinson & 14.5& 3.426& 3.55& 0.01& 0.995& 8.3& 0.344& 0.397& 0.204& 0.897\\
Victoria       & 10.9& 2.249& 2.24& 0.029& 0.992& 4.4& 0.365& 0.361& 0.201& 0.933\\
Patricia Bay   & 12.0& 2.589& 2.685& 0.021& 0.991& 7.4& 0.307& 0.356& 0.216& 0.894\\
Campbell River & 11.6& 3.219& 3.247& 0.016& 0.996& 6.9& 0.341& 0.38& 0.188& 0.915\\
\hline
Dec 2012-CGRF& & & & & & & & & & \\
Point Atkinson & 11.0& 3.362& 3.432& 0.007& 0.997& 5.7& 0.274& 0.273& 0.219& 0.929\\
Victoria       & 12.9& 2.146& 2.111& 0.036& 0.99& 4.7& 0.282& 0.256& 0.175& 0.934\\
Patricia Bay   & 12.8& 2.551& 2.571& 0.024& 0.993& 5.2& 0.275& 0.255& 0.185& 0.934\\
Campbell River & 12.1& 3.064& 3.106& 0.013& 0.996& 8.4& 0.188& 0.263& 0.216& 0.849\\
\hline
Dec 2012-HRDPS& & &  &  &  &  &  &  &  &  \\
Point Atkinson &  10.5&  3.362&  3.42&  0.007&  0.998&  6.2&  0.274&  0.26&  0.231&  0.921\\
Victoria       &  12.6&  2.146&  2.113&  0.035&  0.99&  4.6&  0.282&  0.258&  0.171&  0.937\\
Patricia Bay   &  12.6& 2.551& 2.575& 0.024& 0.993& 5.0& 0.275& 0.26& 0.175& 0.94\\
Campbell River & 12.1& 3.064& 3.104& 0.014& 0.996& 8.1& 0.188& 0.26& 0.218& 0.854\\
\hline
\hline
Averages& & & & & & & & & & \\
Point Atkinson & 11.6&	3.401&	3.483&	0.013&	0.995&	6.7&	0.302&	0.307	&0.192	&0.932\\
Victoria       &10.8&	2.175	&2.162	&0.04	&0.989	&5.1	&0.29	&0.28&	0.167&	0.94\\
Patricia Bay   &11.6&	2.573&	2.619&	0.028&	0.991&	6.0&	0.281&	0.279&	0.179&	0.932\\
Campbell River & 11.6&	3.139&	3.177&	0.021&	0.994&	7.8&	0.246&	0.293&	0.188&	0.893\\
\hline
\end{tabular}}
\label{tab:statistics}
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper production.ipynb and saved in statistics_feb2006.CV 
%I also have standard deviations, correlations, ...

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{{\color{red}Comparison of observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson (top), Sandheads (middle) and NOAA Buoy 46087 (bottom). Observed winds shown in solid black, low resolution CGRF model in dashed black and high resolution model in grey. Observations from Sandheads and Point Atkinson are from the Environment Canada Climate Data archives \citep{ECClimateArchive}.  Observations at the NOAA Buoy are found at this url: \url{http://www.ndbc.noaa.gov/station_page.php?station=46087}. Wind direction represents the direction that the wind is headed.} }
\label{fig:dec2012_weather}
\end{figure}
